Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-16 paper/paper.tex
Spelling correction.

One way this method could be applied to the cylinders is to first divide the cylinders by size. The smaller cylinders can be used with a space-partioning data structure with smaller partitions and the larger ones pun in another space partitioning structure of just put in a list and checked at each iteration.

>>>>

One way this method could be applied to the cylinders is to first divide the cylinders by size. The smaller cylinders can be used with a space-partioning data structure with smaller partitions and the larger ones put in another space partitioning structure of just put in a list and checked at each iteration.
